Look, we can do something

### 2024-11-14 paper.tex
Awesomeness -> Narrowness + update plots (1/2)
Awesomeness -> Narrowness (2/2)

Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
shape parameter we call ``\highlight{awesomeness}'':
\begin{equation}
  \begin{aligned}
    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2 : 2
    L_{AB} \ge cP \}
  \end{aligned}
  \label{eq:awesomeness}
\end{equation}
where, again, $E$ and $B$ are the elongation and the boundary of the pore,
$\rho_{AB}$ is the Euclidean distance between points $A$ and $B$ and $L_{AB}$ is
the length of a path (the shortest one) between $A$ and $B$ along the boundary.

\section{Computational algorithm}
\label{seq:alg}
Our algorithm for calculating \highlight{awesomeness} is quite simple. It
assumes that an image of a pore is made with sufficient resolution, so we can
use boundary pixels without any additional processing. The main algorithm
consists of three parts and is shown in \cref{alg:main}.
\begin{algorithm}[H]
  \caption{Algorithm for computation of \highlight{awesomeness} of a pore.}
  \label{alg:main}
  \begin{algorithmic}[1]
    \Procedure{\texttt{awesomeness}}{\texttt{img}}
    \State \texttt{bs $\gets$ boundary(img)}
    \Comment Construct a list of boundary points (\cref{alg:extraction}).
    \State \texttt{\%bs $\gets$ sort(bs)}
    \Comment Sort points as described in \cref{alg:sort}.
    \State \textbf{return} \texttt{m $\cdot$ pmin(\%bs)}
    \Comment The final step is in \cref{alg:pmin}. \texttt{m} is the fraction in
    \cref{eq:awesomeness}.
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

Finaly, the function \texttt{pmin} is described in \cref{alg:pmin}. This
algorithms assumes that there are enough boundary points in an image. If, for
example, an image is taken with bad resolution (i.e. pores consist only of a few
pixels) some quality improving techniques must be applied first. It also
exploits the commutative property $p_{AB} = p_{BA}$.
\begin{algorithm}[H]
  \caption{The last step of the algorithm for awesomeness: the function \texttt{pmin}.}
  \label{alg:pmin}
  \begin{algorithmic}[1]
    \Procedure{\texttt{pairwise\_distances}}{\texttt{points}}
    \State \textbf{return} \texttt{map(dist, points, tail(points))}
    \Comment Return the Euclidean distance between $i$-th and $i+1$-th
    points. The function \texttt{dist} calculates the distance between two
    points.
    \EndProcedure
    \Procedure{\texttt{perimeter}}{\texttt{points, c}}
    \State \texttt{p1 $\gets$ foldl1((+), pairwise\_distances(points))}
    \State \texttt{p2 $\gets$ dist(head(points), last(points))}
    \State \textbf{return} \texttt{p1 + p2}
    \EndProcedure
    \Procedure{\texttt{minimize\_on\_head}}{\texttt{acc, p, bds, points}}
    \Comment \texttt{acc} is the best (minimal) parameter found so far,
    \texttt{p} is a perimeter of the boundary, \texttt{bds} is a list of
    distances along the boundary from the head of \texttt{points} to all points
    in \texttt{tail(points)}.
    \Procedure{\texttt{go}}{\texttt{acc, x}}
    \State \texttt{(point, bd) $\gets$ x}
    \State \texttt{\%bd $\gets$ min(bd, p - bd)}
    \If{\texttt{\%bd < c/2 $\cdot$ p}}
    \State \textbf{return} \texttt{acc}
    \Else
    \State \texttt{param $\gets$ dist(point, head(points)) / \%bd}
    \State \textbf{return} \texttt{min(acc, param)}
    \EndIf
    \EndProcedure
    \State \texttt{tmp $\gets$ zip(tail(points), ds)}
    \State \textbf{return} \texttt{foldl(go, acc, tmp)}
    \EndProcedure
    \Procedure{\texttt{pmin}}{\texttt{points}}
    \State \texttt{p $\gets$ perimeter(points)}
    \State \texttt{bds $\gets$ scanl1((+), pairwise\_distances(points))}
    \Procedure{\texttt{go}}{\texttt{acc, points}}
    \State \texttt{(param, bds) $\gets$ acc}
    \State \texttt{\%param $\gets$ minimize\_on\_head(param, p, bds, points)}
    \State \texttt{\%bds  $\gets$ map(subtract(head(bds)), tail(bds))}
    \Comment $L_{B_2B_3} = L_{B_1B_3} - L_{B_1B_2}$ if $B_1 < B_2 < B_3$.
    \State \textbf{return} \texttt{(\%param, \%bds)}
    \EndProcedure
    \State \textbf{return} \texttt{foldl(go, (+Inf, bds), tails(points))}
    \Comment For a list \texttt{a = [1,2,3]} \texttt{tails(a)} returns
    \texttt{[[1,2,3], [2,3], [3]]}.
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

The parameter \cref{eq:awesomeness} is scale- and rotation-invariant. The
algorithm presented in this paper changes the parameter by about 10\% when
rotating an image of a pore or scaling it by a factor $0.5-2$ (see
\cref{fig:rotation-resize}). This inaccuracy is OK for assessing quality of pore
clusterization, as can be seen in the next section.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/rotation-resize.png}
  \caption[]{\highlight{Awesomeness} parameter for the same image under rotation
  (red X marks) and resize (blue dot marks) transforms.}
  \label{fig:rotation-resize}
\end{figure}

\section{Results}
We computed \highlight{awesomeness} for 4000 synthetically generated images with
dimensions $1000 \times 1000$ pixels (1000 images from 4 different
datasets). The datasets have the following properties:
\begin{itemize}
\item \texttt{normal}: ``Normal'' pores with convexity $0.5-0.8$.
\item \texttt{mnist}: Pores which resemble digits (still being 1-connected).
\item \texttt{thin}: Pores with low convexity ($< 0.5$) which resemble thin
  stripes.
\item \texttt{mostlyconvex}: Pores with convexity close to $1$.
\end{itemize}
Figure \ref{fig:pores} depicts a pore from each dataset.
\begin{figure}
  \centering
  \subfigure[\texttt{normal}]{
    \includegraphics[width=0.4\linewidth,frame]{images/normal.png}}
  \subfigure[\texttt{thin}]{
    \includegraphics[width=0.4\linewidth,frame]{images/thin.png}}
  \vskip\baselineskip
  \subfigure[\texttt{mnist}]{
    \includegraphics[width=0.4\linewidth,frame]{images/mnist.png}}
  \subfigure[\texttt{mostlyconvex}]{
    \includegraphics[width=0.4\linewidth,frame]{images/mostlyconvex.png}}
  \caption[]{One pore from each dataset used for calculation of
    \texttt{awesomeness}.}
  \label{fig:pores}
\end{figure}

Summarly 3901 images out of 4000 (97.5\%) were good enough for \texttt{sort} to
sort boundary points in pores. For these images we also computed commonly used
convexity and elongation parameters. On \cref{fig:cae-space} each pore is
represented as a dot in convexity-elongation-\highlight{awesomeness} (CEA)
space.
\begin{figure*}
  \centering
  \subfigure[Convexity-elongation-\highlight{awesomeness} space]{
    \includegraphics[width=0.4\linewidth]{images/cae.png}
    \label{fig:cae-space}}
  \hfill
  \subfigure[Convexity-elongation-roundness space]{
    \includegraphics[width=0.4\linewidth]{images/cer.png}
    \label{fig:cer-space}}
  \vskip\baselineskip
  \subfigure[Elongation-\highlight{Correlated awesomeness} space]{
    \includegraphics[width=0.4\linewidth]{images/ae.png}
    \label{fig:ae-space}}
  \caption[]{Synthetically generated pores shown as points in different
    parameter spaces.}
  \label{fig:parameter-spaces}
\end{figure*}

It can be seen that if a pore has low convexity ($< 0.6$)
\highlight{awesomeness} adds no information to the pore's descriptors because it
stays relatively low for all pores. When, however, the convexity is high it adds
a new dimension to the parameter space.

Another common parameter for describing pore shapes is roundness. Figure
\ref{fig:cer-space} features convexity-elongation-roundness (CER) space.
It can be seen that roundness-convexity correlation is bigger than
awesomeness-convexity correlation. All correlation values are in
\cref{tab:correlations}.

On \cref{fig:ae-space} pores are shown in $p-E$ space where $p$ is a
``correlated'' \highlight{awesomeness} parameter \cref{eq:pre-awesomeness}. It
shows that our assumption on the maximal value of \highlight{awesomeness} is
correct indeed.

\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Awesomeness & Elongation & Convexity & Roundness \\
    \hline
    Awesomeness & 1 & 0.049 & 0.557 & 0.745 \\
    \hline
    Elongation & & 1 & 0.457 & 0.355 \\
    \hline
    Convexity &&& 1 & 0.922 \\
    \hline
    Roundness &&&& 1 \\
    \hline
  \end{tabular}
  \caption{Correlation between shape describing parameters.}
  \label{tab:correlations}
\end{table*}

To test abilities of the awesomeness parameter we now divide our pores in groups
with different convexity. The first group has pores with convexity $0.55 \le C < 0.65$,
the second -- $0.65 \le C < 0.75$, the third -- $0.75 \le C < 0.85$ and the fourth
-- $0.85 \le C < 0.95$. Five images with the biggest awesomeness and five images
with the smallest awesomeness from each group are shown on
\cref{fig:convexity-groups-score}. It can be clearly seen that pores with higher
values of \highlight{awesomeness} are more ``solid'' and more finely
clusterized.

For comparison, we do the same sorting across groups for roundness
parameter. The results are on
\cref{fig:convexity-groups-roundness}. Well-clusterized pores have the biggest
roundness for convexity $C > 0.8$. For lower convexity, however, even pores with
the biggest roundness in the group are also underclusterized while
\highlight{awesomeness} parameter is capable of separating well-clusterized and
underclusterized pores.
\begin{figure*}
  \centering
  \subfigure[$0.55 \le C < 0.65$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.60.png}
    \label{fig:small-gap}}
  \hfill
  \subfigure[$0.65 \le C < 0.75$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.70.png}}
  \vskip\baselineskip
  \subfigure[$0.75 \le C < 0.85$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.80.png}}
  \hfill
  \subfigure[$0.85 \le C < 0.95$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.90.png}
    \label{fig:small-blob}}
  \caption[]{Pores divided into groups by their convexity. Upper row of each
    subfigure: pores with minimal \highlight{awesomeness} in the group, lower
    row: pores with maximal \highlight{awesomeness} in the group.}
  \label{fig:convexity-groups-score}
\end{figure*}

@@

Summarizing, we can divide pores into three groups by the quality of
clusterization (see \cref{tab:ranges}).
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    \highlight{Awesomeness} & Comment \\
    \hline
    < 0.1 & Virtually many different pores connected by thin chords \\
    \hline
    0.1 - 0.6 & Pores which can be divides into subpores \\
    \hline
    > 0.6 & Well-clusterized pores \\
    \hline
  \end{tabular}
  \caption{Different values of \highlight{awesomeness} and their meaning.}
  \label{tab:ranges}
\end{table*}

@@

Flaws of this parameter include:
\begin{itemize}
\item Sometimes the shortest path between two points on a pore's boundary either:
  \begin{itemize}
  \item has more than two common points with the boundary;
  \item lies entirely in the pore's exterior (with exception of end points).
  \end{itemize}
  In this case the two points definitely cannot form a bottleneck.
\item C-shaped pores with a small gap, like the pore on the left-top of
  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
  are otherwise clusterized correctly.
\end{itemize}

The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
which does not cross the pore's boundary (see \cref{fig:improved}). Although the
resulting algorithm will have the same $O(n^2)$ complexity, doing so can
increase computational time significantly. We call the parameter $P'$ with
$d_{AB}$ in the place of $\rho_{AB}$ ``improved awesomeness''. The following
relation always holds: $0 < P \le P' \le 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth,frame]{images/improved.png}
  \caption[]{Pairs of points responsible for \highlight{awesomeness} (red) and
    improved \highlight{awesomeness} (green).}
  \label{fig:improved}
\end{figure}

We present an opensource solution for calculating \highlight{awesomeness} and
improved \highlight{awesomeness}. \highlight{E-mail us and buy us coffee so we
  can send this super program to you, no matter where you live! Hurry, this is a
limited offer!} An average time for calculating \highlight{awesomeness} is 1
second for a $1000 \times 1000$ png image and is $1-60$ seconds for calculating
improved \highlight{awesomeness}.

>>>>

Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
shape parameter we call ``narrowness'':
\begin{equation}
  \begin{aligned}
    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2 : 2
    L_{AB} \ge cP \}
  \end{aligned}
  \label{eq:awesomeness}
\end{equation}
where, again, $E$ and $B$ are the elongation and the boundary of the pore,
$\rho_{AB}$ is the Euclidean distance between points $A$ and $B$ and $L_{AB}$ is
the length of a path (the shortest one) between $A$ and $B$ along the boundary.

\section{Computational algorithm}
\label{seq:alg}
Our algorithm for calculating narrowness is quite simple. It assumes that an
image of a pore is made with sufficient resolution, so we can use boundary
pixels without any additional processing. The main algorithm consists of three
parts and is shown in \cref{alg:main}.
\begin{algorithm}[H]
  \caption{Algorithm for computation of narrowness of a pore.}
  \label{alg:main}
  \begin{algorithmic}[1]
    \Procedure{\texttt{narrowness}}{\texttt{img}}
    \State \texttt{bs $\gets$ boundary(img)}
    \Comment Construct a list of boundary points (\cref{alg:extraction}).
    \State \texttt{\%bs $\gets$ sort(bs)}
    \Comment Sort points as described in \cref{alg:sort}.
    \State \textbf{return} \texttt{m $\cdot$ pmin(\%bs)}
    \Comment The final step is in \cref{alg:pmin}. \texttt{m} is the fraction in
    \cref{eq:awesomeness}.
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

Finaly, the function \texttt{pmin} is described in \cref{alg:pmin}. This
algorithms assumes that there are enough boundary points in an image. If, for
example, an image is taken with bad resolution (i.e. pores consist only of a few
pixels) some quality improving techniques must be applied first. It also
exploits the commutative property $p_{AB} = p_{BA}$.
\begin{algorithm}[H]
  \caption{The last step of the algorithm for narrowness: the function
    \texttt{pmin}.}
  \label{alg:pmin}
  \begin{algorithmic}[1]
    \Procedure{\texttt{pairwise\_distances}}{\texttt{points}}
    \State \textbf{return} \texttt{map(dist, points, tail(points))}
    \Comment Return the Euclidean distance between $i$-th and $i+1$-th
    points. The function \texttt{dist} calculates the distance between two
    points.
    \EndProcedure
    \Procedure{\texttt{perimeter}}{\texttt{points, c}}
    \State \texttt{p1 $\gets$ foldl1((+), pairwise\_distances(points))}
    \State \texttt{p2 $\gets$ dist(head(points), last(points))}
    \State \textbf{return} \texttt{p1 + p2}
    \EndProcedure
    \Procedure{\texttt{minimize\_on\_head}}{\texttt{acc, p, bds, points}}
    \Comment \texttt{acc} is the best (minimal) parameter found so far,
    \texttt{p} is a perimeter of the boundary, \texttt{bds} is a list of
    distances along the boundary from the head of \texttt{points} to all points
    in \texttt{tail(points)}.
    \Procedure{\texttt{go}}{\texttt{acc, x}}
    \State \texttt{(point, bd) $\gets$ x}
    \State \texttt{\%bd $\gets$ min(bd, p - bd)}
    \If{\texttt{\%bd < c/2 $\cdot$ p}}
    \State \textbf{return} \texttt{acc}
    \Else
    \State \texttt{param $\gets$ dist(point, head(points)) / \%bd}
    \State \textbf{return} \texttt{min(acc, param)}
    \EndIf
    \EndProcedure
    \State \texttt{tmp $\gets$ zip(tail(points), ds)}
    \State \textbf{return} \texttt{foldl(go, acc, tmp)}
    \EndProcedure
    \Procedure{\texttt{pmin}}{\texttt{points}}
    \State \texttt{p $\gets$ perimeter(points)}
    \State \texttt{bds $\gets$ scanl1((+), pairwise\_distances(points))}
    \Procedure{\texttt{go}}{\texttt{acc, points}}
    \State \texttt{(param, bds) $\gets$ acc}
    \State \texttt{\%param $\gets$ minimize\_on\_head(param, p, bds, points)}
    \State \texttt{\%bds  $\gets$ map(subtract(head(bds)), tail(bds))}
    \Comment $L_{B_2B_3} = L_{B_1B_3} - L_{B_1B_2}$ if $B_1 < B_2 < B_3$.
    \State \textbf{return} \texttt{(\%param, \%bds)}
    \EndProcedure
    \State \textbf{return} \texttt{foldl(go, (+Inf, bds), tails(points))}
    \Comment For a list \texttt{a = [1,2,3]} \texttt{tails(a)} returns
    \texttt{[[1,2,3], [2,3], [3]]}.
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

The parameter \cref{eq:awesomeness} is scale- and rotation-invariant. The
algorithm presented in this paper changes the parameter by about 10\% when
rotating an image of a pore or scaling it by a factor $0.5-2$ (see
\cref{fig:rotation-resize}). This inaccuracy is OK for assessing quality of pore
clusterization, as can be seen in the next section.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/rotation-resize.png}
  \caption[]{Narrowness parameter for the same image under rotation (red X
    marks) and resize (blue dot marks) transforms.}
  \label{fig:rotation-resize}
\end{figure}

\section{Results}
We computed narrowness for 4000 synthetically generated images with dimensions
$1000 \times 1000$ pixels (1000 images from 4 different datasets). The datasets
have the following properties:
\begin{itemize}
\item \texttt{normal}: ``Normal'' pores with convexity $0.5-0.8$.
\item \texttt{mnist}: Pores which resemble digits (still being 1-connected).
\item \texttt{thin}: Pores with low convexity ($< 0.5$) which resemble thin
  stripes.
\item \texttt{mostlyconvex}: Pores with convexity close to $1$.
\end{itemize}
Figure \ref{fig:pores} depicts a pore from each dataset.
\begin{figure}
  \centering
  \subfigure[\texttt{normal}]{
    \includegraphics[width=0.4\linewidth,frame]{images/normal.png}}
  \subfigure[\texttt{thin}]{
    \includegraphics[width=0.4\linewidth,frame]{images/thin.png}}
  \vskip\baselineskip
  \subfigure[\texttt{mnist}]{
    \includegraphics[width=0.4\linewidth,frame]{images/mnist.png}}
  \subfigure[\texttt{mostlyconvex}]{
    \includegraphics[width=0.4\linewidth,frame]{images/mostlyconvex.png}}
  \caption[]{One pore from each dataset used for calculation of narrowness.}
  \label{fig:pores}
\end{figure}

Summarly 3901 images out of 4000 (97.5\%) were good enough for \texttt{sort} to
sort boundary points in pores. For these images we also computed commonly used
convexity and elongation parameters. On \cref{fig:cae-space} each pore is
represented as a dot in convexity-elongation-narrowness (CEN) space.
\begin{figure*}
  \centering
  \subfigure[Convexity-elongation-narrowness space]{
    \includegraphics[width=0.4\linewidth]{images/cae.png}
    \label{fig:cae-space}}
  \hfill
  \subfigure[Convexity-elongation-roundness space]{
    \includegraphics[width=0.4\linewidth]{images/cer.png}
    \label{fig:cer-space}}
  \vskip\baselineskip
  \subfigure[Elongation-Correlated narrowness space]{
    \includegraphics[width=0.4\linewidth]{images/ae.png}
    \label{fig:ae-space}}
  \caption[]{Synthetically generated pores shown as points in different
    parameter spaces.}
  \label{fig:parameter-spaces}
\end{figure*}

It can be seen that if a pore has low convexity ($< 0.6$) narrowness adds no
information to the pore's descriptors because it stays relatively low for all
pores. When, however, the convexity is high it adds a new dimension to the
parameter space.

Another common parameter for describing pore shapes is roundness. Figure
\ref{fig:cer-space} features convexity-elongation-roundness (CER) space. It can
be seen that roundness-convexity correlation is bigger than narrowness-convexity
correlation. All correlation values are in \cref{tab:correlations}.

On \cref{fig:ae-space} pores are shown in $p-E$ space where $p$ is a
``correlated'' narrowness parameter \cref{eq:pre-awesomeness}. It shows that our
assumption on the maximal value of narrowness is correct indeed.

\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Narrowness & Elongation & Convexity & Roundness \\
    \hline
    Narrowness & 1 & 0.106 & 0.611 & 0.0.800 \\
    \hline
    Elongation & & 1 & 0.457 & 0.355 \\
    \hline
    Convexity &&& 1 & 0.922 \\
    \hline
    Roundness &&&& 1 \\
    \hline
  \end{tabular}
  \caption{Correlation between shape describing parameters.}
  \label{tab:correlations}
\end{table*}

To test abilities of the narrowness parameter we now divide our pores in groups
with different convexity. The first group has pores with convexity
$0.55 \le C < 0.65$, the second -- $0.65 \le C < 0.75$, the third --
$0.75 \le C < 0.85$ and the fourth -- $0.85 \le C < 0.95$. Five images with the
biggest narrowness and five images with the smallest narrowness from each group
are shown on \cref{fig:convexity-groups-score}. It can be clearly seen that
pores with higher values of narrowness are more ``solid'' and more finely
clusterized.

For comparison, we do the same sorting across groups for roundness
parameter. The results are on
\cref{fig:convexity-groups-roundness}. Well-clusterized pores have the biggest
roundness for convexity $C > 0.8$. For lower convexity, however, even pores with
the biggest roundness in the group are also underclusterized while narrowness
parameter is capable of separating well-clusterized and underclusterized pores.
\begin{figure*}
  \centering
  \subfigure[$0.55 \le C < 0.65$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.60.png}
    \label{fig:small-gap}}
  \hfill
  \subfigure[$0.65 \le C < 0.75$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.70.png}}
  \vskip\baselineskip
  \subfigure[$0.75 \le C < 0.85$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.80.png}}
  \hfill
  \subfigure[$0.85 \le C < 0.95$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.90.png}
    \label{fig:small-blob}}
  \caption[]{Pores divided into groups by their convexity. Upper row of each
    subfigure: pores with minimal narrowness in the group, lower row: pores with
    maximal narrowness in the group.}
  \label{fig:convexity-groups-score}
\end{figure*}

@@

Summarizing, we can divide pores into three groups by the quality of
clusterization (see \cref{tab:ranges}).
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    \highlight{Narrowness} & Comment \\
    \hline
    < 0.1 & Virtually many different pores connected by thin chords \\
    \hline
    0.1 - 0.6 & Pores which can be divides into subpores \\
    \hline
    > 0.6 & Well-clusterized pores \\
    \hline
  \end{tabular}
  \caption{Different values of narrowness and their meaning.}
  \label{tab:ranges}
\end{table*}

@@

Flaws of this parameter include:
\begin{itemize}
\item Sometimes the shortest path between two points on a pore's boundary either:
  \begin{itemize}
  \item has more than two common points with the boundary;
  \item lies entirely in the pore's exterior (with exception of end points).
  \end{itemize}
  In this case the two points definitely cannot form a bottleneck.
\item C-shaped pores with a small gap, like the pore on the left-top of
  \cref{fig:small-gap} always have small narrowness, even if they are otherwise
  clusterized correctly.
\end{itemize}

The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
which does not cross the pore's boundary (see \cref{fig:improved}). Although the
resulting algorithm will have the same $O(n^2)$ complexity, doing so can
increase computational time significantly. We call the parameter $P'$ with
$d_{AB}$ in the place of $\rho_{AB}$ ``improved narrowness''. The following
relation always holds: $0 < P \le P' \le 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth,frame]{images/improved.png}
  \caption[]{Pairs of points responsible for narrowness (red) and improved
    narrowness (green).}
  \label{fig:improved}
\end{figure}

We present an opensource solution for calculating narrowness and improved
narrowness. \highlight{E-mail us and buy us coffee so we can send this super
  program to you, no matter where you live! Hurry, this is a limited offer!} An
average time for calculating narrowness is 1 second for a $1000 \times 1000$ png
image and is $1-60$ seconds for calculating improved narrowness.
